Analysis

### 2023-05-03 analysis/alt_analysis.Rmd

The actual model consists of a nimble code block that describes the relationships and sets the priors for the parameters. It should be noted that we have changed the function for the number of settlements, and thus the proposal distribution. It is now a Negative Binomial Distribution, where both the expected value and the variance can vary. The expected value is still derived from $\lambda_t$, but this is integrated into the model via a success parameter $prob_t$, which results as follows:

$$
prob_t = \frac{r}{r+\lambda_t}
$$

@@

  # Estimate the initial state vector of population abundances
  nEnd ~ dnorm(nSites[nYears] * MeanSiteSize / AreaSwissPlateau, sd=0.5)

  # Autoregressive process for remaining years
  for(t in 2:(nYears)) {
    # The actual number of sites per year
    nSites[t] ~ dnegbin(prob[t],r)
    prob[t] <- r/(r+lambda[t])

    # limiting the change to a maximum value, estimated in the model
    constraint_lambda_lower[t] ~ dconstraint(
      nSites[t]/nSites[t-1] < (max_growth_rate + 1)
      )
    constraint_lambda_upper[t] ~ dconstraint(
      nSites[t-1]/nSites[t] < (max_growth_rate + 1)
      )
  }

@@

Finally, we have to define which parameters (apart from the top-level stochastic nodes of the model) are to be observed and stored. We also include the population density as a core parameter and the relative proportion of proxies p:

```{r}
model_monitors <- c("PopDens", "p", "r")
```

@@

```{r}
ggsave(normalizePath(file.path(here(), "figures","p_estimation_neg_binomial.pdf"), mustWork = F),
       plot = p_plot, width = 21, height = 29.7/2, units = "cm")
```
Also interesting is the variation coefficient from the estimation of the Population density:

>>>>

The actual model consists of a nimble code block that describes the relationships and sets the priors for the parameters. It should be noted that we have changed the function for the number of settlements, and thus the proposal distribution. It is now a Negative Binomial Distribution, where both the expected value and the variance can vary. The expected value is still derived from $\lambda_t$, but this is integrated into the model via a success parameter $p_t$, which results as follows:

$$
p_t = \frac{r}{r+\lambda_t}
$$

@@

  # Estimate the initial state vector of population abundances
  nEnd ~ dnorm(z[nYears] * MeanSiteSize / AreaSwissPlateau, sd=0.5)

  # Autoregressive process for remaining years
  for(t in 2:(nYears)) {
    # The actual number of sites per year
    z[t] ~ dnegbin(p[t],r)
    p[t] <- r/(r+lambda[t])

    # limiting the change to a maximum value, estimated in the model
    constraint_lambda_lower[t] ~ dconstraint(
      z[t]/z[t-1] < (max_growth_rate + 1)
      )
    constraint_lambda_upper[t] ~ dconstraint(
      z[t-1]/z[t] < (max_growth_rate + 1)
      )
  }

@@

Finally, we have to define which parameters (apart from the top-level stochastic nodes of the model) are to be observed and stored. We also include the population density as a core parameter and the relative proportion of proxies beta:

```{r}
model_monitors <- c("PopDens", "beta", "r")
```

@@

```{r}
ggsave(normalizePath(file.path(here(), "figures","beta_estimation_neg_binomial.pdf"), mustWork = F),
       plot = beta_plot, width = 21, height = 29.7/2, units = "cm")
```
Also interesting is the variation coefficient from the estimation of the Population density:

### 2023-05-03 analysis/analysis.Rmd

```{r message=FALSE}
library(tidyverse)
library(ggdist)
library(reshape2)
library(here)
library(RcppRoll)
library(sf)
library(ggspatial)
library(vegan)
library(neotoma)
library(analogue)
library(rcarbon)
library(doParallel)
library(nimble)
library(coda)
library(MCMCvis)
library(fmcmc)
```

>>>>

```{r message=FALSE}
library(tidyverse)
library(ggdist)
library(reshape2)
library(here)
library(RcppRoll)
library(sf)
library(ggspatial)
library(vegan)
library(neotoma)
library(analogue)
library(rcarbon)
library(doParallel)
library(nimble)
library(coda)
library(MCMCvis)
library(fmcmc)
library(grid)
```
